\documentclass[10pt]{article}
\usepackage[a4paper, total={6in,10in}]{geometry}

\title{COMS 3007\\ Tutorial 1}
\author{Takatso Molekane: 569869}
\date{10 February 2019}

\begin{document}
	\maketitle
	
	\begin{enumerate}
	\item
		\begin{enumerate}
			\item Supervised learning (Classification); this is because we need to teach our algorithm to identify glasses.
			\item Reinforcement learning. Because we want to win the game with minimum moves and thus greater reward.
			\item Supervised learning (Classification); our algorithm needs to learn the different types of vehicles.
			\item Supervised learning (Classification); the judgement of a court case is based on the previous court case's verdict. (Training Data).
			\item Supervised learning (Classification); the student will either pass or fail based on the marks they've been getting throughout the semester.
			\item Supervised learning (Classifiction); we first need  to know the living condtitions of the patient, then we can come up with the best plan.
			\item Reinforcement learnng. The game should be able to by interacting with the other player.
			\item Supervised learning (Regression). BitCoin price is continuous and to predict its price we need to know previous prices.
		\end{enumerate}
		
	\item Facebook ads. Facebook shows me ads based on the sites I have been looking and the types of pages I have liked.
	
	\item Pick and Pay Smart shopper. They learn everytime I swipe my smart shopper card what items I like to buy. Sometimes with that information they give me special offers on selected items.
	
	\item 
		\begin{enumerate}
			\item Physical Classification 
				\begin{enumerate}
					\item Sound.
					\item Teeth.
					\item Body size.
					\item Eyes.
					\item Ears.
					\item Walk.
					\item Face.
					\item Posture.
				\end{enumerate}
			\item Image Classification
				\begin{enumerate}
					\item Ears.
					\item Eyes.
					\item Face.
					\item Teeth.
					\item Posture.
				\end{enumerate}

			\item Predicting the flight speed of a bird.
				\begin{enumerate}
					\item Size of wings.
					\item Distance from the ground.
					\item Size of the bird.
					\item Size of limbs.
				\end{enumerate}
			\item Predicting student performance.
				\begin{enumerate}
					\item Number of submissions.
					\item Class attendance.
					\item Class participation.
					\item Hours spend studying.
					\item Class participation.
				\end{enumerate}
			\item Classifying Songs by Genre
				\begin{enumerate}
					\item Tempo
					\item Pitch
					\item BPM
					\item Instruments
					\item Artist
				\end{enumerate}
			\item Predict winning team.
				\begin{enumerate}
					\item Games Won
					\item Coach
					\item Striker
					\item Defence Strength
				\end{enumerate}
			\item Predict number of chocolate sales
				\begin{enumerate}
					\item Price
					\item Size
				\end{enumerate}
		\end{enumerate}
	\end{enumerate}
	
	
	
\end{document}